 

### 2021-09-01 vertical-thermal-review_SI.Rmd
knit in tealeaves parameters table
@NidhiVinod , FYI, and a question: did you use all of these, or just a subset? And is there a table of other parameters?
select & order columns for table

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(flextable)
set_flextable_defaults(font.family = "Arial", font.size = 9)
parameters_table <- read.csv("NEON_height_profiles/HARV_neon_stats.csv", stringsAsFactors = FALSE, check.names = FALSE)
parameters_table <- parameters_table[c(9, 1, 3:6)] #select and order columns for inclusion
ft <- flextable(parameters_table)
ft <- autofit(ft)
ft
```
